Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2024-06-14 Paper.tex
eip-4895-alexprut-review

The process of finalising a block involves two stages:

@@

\subsection{Executing Withdrawals}
After processing the block's transactions, the withdrawals are executed. A withdrawal is simply an increase of the recipient account's balance of the specified amount. No other balances are decreased, a withdrawal is not a transfer but a creation of funds.
A withdrawal operation cannot fail and has no gas cost. We define the function $P$ as the withdrawal state transition function:

\begin{eqnarray}
P(\boldsymbol{\sigma}_w, W) & \equiv & \boldsymbol{\sigma}_{w+1} \\
\boldsymbol{\sigma}_{w+1} & \equiv & \boldsymbol{\sigma}_w \quad \text{except:} \\
\boldsymbol{\sigma}_{w+1}[W_r]_{\mathrm{b}} & \equiv & \boldsymbol{\sigma}_{w}[W_r]_{\mathrm{b}} + (W_a \times 10^9)
\end{eqnarray}

@@

\begin{equation}
K(\boldsymbol{\sigma}, B) \equiv P(P(\boldsymbol{\sigma}, W_0), W_1) ...
\end{equation}

>>>>

The process of finalising a block involves three stages:

@@

\subsection{Executing Withdrawals}
After processing the block's transactions, the withdrawals are executed. A withdrawal is simply an increase of the recipient account's balance of the specified Gwei amount. No other balances are decreased, a withdrawal is not a transfer but a creation of funds.
A withdrawal operation cannot fail and has no gas cost. We define the function $E$ as the withdrawal state transition function:

\begin{eqnarray}
E(\boldsymbol{\sigma}_w, W) & \equiv & \boldsymbol{\sigma}_{w+1} \\
\boldsymbol{\sigma}_{w+1} & \equiv & \boldsymbol{\sigma}_w \quad \text{except:} \\
\boldsymbol{\sigma}_{w+1}[W_r]_{\mathrm{b}} & \equiv & \boldsymbol{\sigma}_{w}[W_r]_{\mathrm{b}} + (W_a \times 10^9)
\end{eqnarray}

@@

\begin{equation}
K(\boldsymbol{\sigma}, B) \equiv E(E(\boldsymbol{\sigma}, W_0), W_1) ...
\end{equation}
